EDA

### 2021-04-23 EDA_OnlineMaskedPriming.Rmd
add > 250 ms filter to EDA Rmd

exp1_data_to_include <- exp1 %>% filter(source %in% exp1_participants_to_include$source & participant %in% exp1_actual_participants$PROLIFIC_PID) %>% mutate(StimulusType = StimulusType %>% factor(levels = c("NW", "WORD"), labels = c("Nonword", "Word")), Condition = Condition %>% factor(levels = c("ID", "UN"), labels = c("Identical", "Unrelated")), PrimeDuration = PrimeDuration %>% factor(levels = c(33, 50), labels = c("33 ms", "50 ms")), rt = rt * 1000)

@@

exp2_data_to_include <- exp2 %>% filter(source %in% exp2_participants_to_include$source & participant %in% exp2_actual_participants$PROLIFIC_PID) %>% mutate(StimulusType = StimulusType %>% factor(levels = c("NW", "WORD"), labels = c("Nonword", "Word")), Condition = Condition %>% factor(levels = c("ID", "UN"), labels = c("Identical", "Unrelated")), PrimeDuration = PrimeDuration %>% factor(levels = c(16, 33), labels = c("16 ms", "33 ms")), rt = rt * 1000)
```

>>>>

exp1_data_to_include <- exp1 %>% 
  filter(source %in% exp1_participants_to_include$source & participant %in% exp1_actual_participants$PROLIFIC_PID) %>% 
  mutate(StimulusType = StimulusType %>% 
           factor(levels = c("NW", "WORD"), labels = c("Nonword", "Word")), Condition = Condition %>% 
           factor(levels = c("ID", "UN"), labels = c("Identical", "Unrelated")), PrimeDuration = PrimeDuration %>% factor(levels = c(33, 50), labels = c("33 ms", "50 ms")), rt = rt * 1000) %>% 
  filter(rt > 250 & rt < 2000)
```

@@

exp2_data_to_include <- exp2 %>% filter(source %in% exp2_participants_to_include$source & participant %in% exp2_actual_participants$PROLIFIC_PID) %>% mutate(StimulusType = StimulusType %>% factor(levels = c("NW", "WORD"), labels = c("Nonword", "Word")), Condition = Condition %>% factor(levels = c("ID", "UN"), labels = c("Identical", "Unrelated")), PrimeDuration = PrimeDuration %>% factor(levels = c(16, 33), labels = c("16 ms", "33 ms")), rt = rt * 1000) %>% filter(rt > 250 & rt < 2000)
